---
title: "Introduction to ExcelStats"
author: "Karl-Gunnar Severinsen"
date: "2025-01-29"
output: html_document
---

# Introduction

ExcelStats is an R package that provides functions to calculate and display descriptive statistics.

## Installation

To install the package, use the following commands in R:

```{r}
# Install devtools if you haven't already
install.packages("devtools")

# Install the package from GitHub
devtools::install_github("kgse/ExcelStat")
```

## Functions

### 1. ExcelStats_df

This function calculates descriptive statistics and returns them as a data frame.
The output is more customisable

### Usage

```{r}
#| warning: false
library(ExcelStats)

# Example data
set.seed(666)  # For reproducibility
df <- tibble(x = sample(1:10, 150, replace = TRUE))

# Calculate descriptive statistics
stats_df <- ExcelStats_df(df, "x")

# Print the data frame
print(stats_df)
```



### 2. ExcelStats_kbl

This function calculates descriptive statistics and returns them as a kable object for easy printing to PDF.

### Usage

```{r}
#| warning: false
library(ExcelStats)

# Example data
set.seed(666)  # For reproducibility
df <- tibble(x = sample(1:10, 150, replace = TRUE))

# Calculate descriptive statistics and print as kable (for .pdf)
stats_kable <- ExcelStats_kbl(df, "x")

# Print the kable object
print(stats_kable)
```


## Conclusion

ExcelStats makes it easy to calculate and display the same descriptive statistics as in Excel in R. 
